\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-08-02 write_up/mixfishsim_ecolmod.tex
Small change

\begin{enumerate}
	\item How does sampling-derived data reflects the underlying community 
		structure? 	
	\item How does data aggregation and source impact on spatial fisheries
	management measures?
\end{enumerate}

@@

\subsection{How does sampling-derived data reflect the underlying population
	structure?}

>>>>

\begin{enumerate}
	\item How does sampling-derived fisheries data reflects the underlying
		community structure? 	
	\item How does data aggregation and source impact on spatial fisheries
	management measures?
\end{enumerate}

@@

\subsection{How does sampling-derived fisheries data reflect the underlying
	population structure?}
